---
output: github_document
editor_options: 
  chunk_output_type: console
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```
# nodegraph

The goal of nodegraph is to provide infrastructure for delaying matrix and 
array operations.

## Installation

``` r
devtools::install_github("DavisVaughan/nodegraph")
```

## Example

nodegraph "remembers" the operations that you perform on your matrix/array,
but doesn't actually perform the computation. It performs all of the computations
at once when you call `compute()`, computing any necessary dependencies and
storing them as it goes.

```{r}
library(nodegraph)
```


Create a `delay_array` to get started.

```{r}
mat <- matrix(1:10)

delay_mat <- as_delay_array(mat)
delay_mat
```

It looks similar to a matrix, but under the hood it's pretty different. Let's
try and do something with it.

```{r}
delay_mat2 <- as_delay_array(matrix(1:10))

res <- delay_mat + delay_mat2
res
```

The output of the `+` operation knows the shape, but not the actual result. This
is because it has not yet been computed.

You can add more operations, and they get chained together. R matrices are
promoted to `delay_array`s before the computation takes place.

```{r}
res2 <- res / matrix(5, nrow = 10)
res2
```

To actually perform the computation, call `compute()`. It will compute any
child dependencies and itself. Along the way, it will set the values so it 
doesn't have to calculate them again.

```{r}
compute(res2)
```

Look, it remembered that `res2` has been computed!

```{r}
res2
```


Look, `res` (a dependency of `res2`) has been computed now too!

```{r}
res
```

## Extensibility

`nodegraph` is being designed with extensibility in mind. If you create a new
class that inherits from `delay_array`, then you can define methods for the
following 2 functions to get the laziness you see here:

* `compute_engine()` - Given a set of _known_ children (arguments), and an operation (like `+`),
this defines how your engine computes the result of that operation.

* `compute_dim_engine()` - Given a set of arguments for an operation (i.e. `x`
and `y` in the expression `x+y`), this defines what the dimension of the output
should be. At first glance, you might think this is the same no matter what
backend you use, but some backends allow for _broadcasting_ which can change
the dimensions substantially. The default method uses R's strict dimensionality
rules.


